\chapter{Blockchain Frameworks}
\label{chap:blockchain-frameworks}

%\minitoc \mtcskip \noindent
Not sure if this would have enough content to be a whole new chapter, it could probably be integrated in the previous one, we'll see.

\todo{fcorreia: don't forget to review the previous paragraph.}

\section{Ethereum}

With the purpose of building a blockchain that does more than just provide a currency system, the Ethereum project was developed and launched in 2014. A white paper, written by Vitalik Buterin was released explaining the concepts and inner-workings of this platform, and its popularity has been growing ever since. Citing Buterin's paper, Ethereum has the intent to \textit{"allow developers to create arbitrary consensus-based applications that have the
scalability, standardization, feature-completeness, ease of development and interoperability" } \cite{Buterin2014}.

\subsection{Smart Contracts}
In short, Ethereum is a blockchain platform that implements a Turing-complete programming language, allowing for the existence of code stored in the form of "contracts". This allows for the practical existence of Smart Contracts, a concept first proposed by Nick Szabo in 1996 \cite{szabo1996smart}. According to Szabo, \textit{"A smart contract is a set of promises, specified in digital form, including protocols within which the parties perform on these promises."} 

\todo{fcorreia: in the above citation: make "A" lowercase and move the final mark to after the closing double quote.}

So, at a more superficial level, a smart contract is just code, a structure that follows pre-specified rules, in order to move around assets, such as cryptocurrency tokens, and change its state. It reacts according to the interactions it has with the other elements of the blockchain, which, in a crude manner, can be either people or other contracts. In other words, Ethereum moves beyond the realm of currency and opens up the possiblity for decentralized applications to be ran directly on the blockchain. 

\todo{fcorreia: could be worth mentioning that the result of applying a contract is still subject to the consensus mechanism. this ties in nicely with what toy explain in the next section, as it is what makes the concept of a "global computer" possible.}

%In general, there are
%two types of accounts: externally owned accounts, controlled by private keys, and contract accounts, controlled
%by their contract code. An externally owned account has no code, and one can send messages from an
%externally owned account by creating and signing a transaction;
%in a contract account, every time the
%contract account receives a message its code activates, allowing it to read and write to internal storage and
%send other messages or create contracts in turn.

\subsection{Currency}

The interesting aspect of Ethereum, however, is that the code from these applications or contracts is executed by the peer-to-peer network nodes, making Ethereum a globally available computer. Of course, with computational power comes a price. Each time a function from a contract is called, someone's computer, a mining node, is doing all the computations, and for each line of code, an agreed fee must be paid. As such, Ethereum has its own cryptocurrency, by the name of Ether, and which is essential to fuel the network.

\subsection{Consensus}

At the moment, Ethereum is still using PoW as the consensus protocol, in a similar fashion to Bitcoin. There are projects currently trying to move Ethereum to PoS, such as Casper \cite{Buterin2017}. PoS is a consensus protocol with a different paradigm, in which the block mining process is roughly based on trust, on the fact that the miner has a certain stake or investment (like cryptocurrency) in the network, and so it is in their best benefit to be an honest node. 

The benefit of PoS over PoW is that there isn't as much waste of computational power as in PoW. In PoW, miners have to intensively search for a target number, which allows them to claim the block as their own. This serves no other scientific or practical purpose other than making the mining process hard, and, as soon as a node successfully mines a block, all the energy used  by all the other mining nodes that were in this process basically goes to waste \cite{Buterin2013}. There are other concerns that make a PoS system like Casper a better option as well, such as performance concerns. 

\todo{fcorreia: to call it "waste" is a bit subjective, as this is a mechanism that fulfill a specific purpose (i.e., it's suppose to have an increasing difficulty for it to work). I do agree that other alternatives can be more computationally and energetically efficient though, and that this is ever more important as the use of these platforms increases, as so does the cost (financial, environmental, etc).}

\subsection{Performance and Scalability}

\paragraph{Latency and Throughput} 

Ever since its conception, there has been concern as to whether Ethereum's \textbf{throughput} and \textbf{latency} are enough to handle a large amount of applications running at once, and if it will be scalable in the future. The recent launch of an application by the name of CryptoKitties disrupted Ethereum, congesting the main network and slowing down the speed of transactions, again raising concern over Ethereum's performance.

These concerns are also very much valid for the case of supply chains. If Ethereum were to be integrated with a supply chain, one of the most important factors to take into account would be exactly the performance and scalability of the system. It is important to note, though, that private and public blockchains have different performances as well as different scalability concerns. Furthermore, certain values that affect the performance (such as the block time) also have an affect on the scalability, and consequently, on the security. This means that these attributes are interdependent and require a fine balance. \todo{pedro: citar paper de performance analysis}

In a public chain, security is a much bigger concern, as there are many different kinds of attacks, and the blockchain's values are balanced in a way that tries to prevent these. Such values can easily be adjusted in a private chain, in ways they can't in a public chain, where they would cause forks, clog the chain or raise security issues. In addition, private blockchain deployments are usually more centralized, concentrating their power in fewer nodes, as there is an inherent sense of trust from within the network. For this very reason, this type of blockchain is more easily scalable as well.

The performance of blockchains such as Ethereum is usually measured by the average throughput, which is the number of processed transactions per second (TPS). This depends a lot on two main factors:
\begin{itemize}
\item The block size - in Ethereum, the block size is not a fixed value; rather, it has a "gas" limit; each transaction put into the block spends some gas, and when the gas reaches the limit for that block, the block is full;
\item The average time to publish a block - block interval; in Bitcoin, this was a fixed 10 minute time, but in Ethereum, this time can be as low as 15 seconds\todo{pedro: citar paper de performance analysis}; this is directly related to the latency, the time a transaction takes to be integrated into the blockchain;
\end{itemize}

The fact that both transactions and block can vary in their size makes it hard to theoretically pinpoint what the performance of an Ethereum network is. In practice, though, and according to recent studies and statistics gathered, the throughput of the main Ethereum network is around 15 TPS %again, o mesmo estudo dá estes valores.

\paragraph{Blockchain Size}
Besides latency and throughput, most blockchains are facing the problem that the size required to store the blockchain itself is becoming increasingly large, and is constantly growing. With this kind of pace, not every node will be able to store the chain in order to validate it.

This easily becomes a security problem for public blockchains, as the power will be concentrated among the few nodes who can store the blockchain. In Ethereum, every node has to process all transactions and store the entire state of the blockchain, \todo{pedro: Citar onde diz isto do Ethereum (era no white paper?)} hence, this is an important issue to address. 

Solutions to the above mentioned issues of the above mentioned issues have already been proposed and are being tested. Some of these are Raiden, Casper, Sharding and Plasma.

\paragraph{Casper}

To put it simply, Casper is a partial consensus mechanism that aims to implement PoS as the consensus algorithm in Ethereum. The way it works, it basically allows anyone who holds anything of value in the system, in this case, the Ethereum currency, Ethers, to participate in choosing the next block.

Casper has the important characteristic of accountability. The validator nodes deposit some of their currency to have a stake on the mining process of a block, so they have their own deposits at stake. Therefore, they are encouraged to be honest, because any violation of the rules or attempts of attack puts them at risk of losing this deposit. The higher the stake, the higher the power: with a high stake, it might be easier to perform an attack, but as it is also a lot riskier, so attacks are discouraged.

Another important aspect of Casper is that, as a PoS based mechanism, it allows for a more efficient Blockchain as it enables miners to work without high end hardware and high electricity costs, while also potentially allowing for lower block times.

\paragraph{Sharding}

Sharding is a solution that aims to increase the throughput of Ethereum. It acts upon the problem problem that every node must validate every transaction, by dividing nodes and transactions into subsets and assigning them such that a subset of the nodes will verify a subset of transactions \cite{ButerinSharding}. This allows for transactions to be processed in parallel, and, as long as there are enough nodes validating a transaction, security is maintained, and more transactions per second are able to be processed, therefore increasing throughput in a scalable way.

\paragraph{Plasma}

\paragraph{Raiden}

\break

\iffalse
\subsection{Usability}
- Explain that, though there is a main ethereum network, it can also be deployed privately

- Examples of companies that Ethereum, either in the public chain, or in a private one

\subsection{Ethereum Applicability to Supply Chain}
Maybe this subsection is already what is described in the sections that follow, such as section 3.5 Applications and so on. Especially in section 3.5, I should explain better how the Applications of Ethereum (section 3.4.4), can be applied in general
- Talk about Eth possible applicability, because of the fact it might be expensive;
\fi

\section{Hyperledger}

Later today (07/02), I'll have an  high level explanation of Hyperledger, Coco and Corda (less focus on these last 2). I'll also try having written 5.2 and 5.3.

Various frameworks from hyperledger, difference

"enables design decisions like sharding and channels to be implemented without much hassle. And since trust is already achieved from outside the network, we do not need much computational power to support that trust. This allows us to use different consensus mechanism, such as BFT protocols, and almost all of the issues public blockchains have, disappears. Furthermore, the governing body can ensure data access to participants in the channel and only allow them to view sensitive transaction data. Thus, Hyperledger Fabric has the features required for modern enterprise security standards, that are difficult to achieve in public
blockchains."

\section{Coco}
"Coco Will be Open Source
Currently, (at the time of writing this) Microsoft has not yet publicly released the Coco Framework. However, Microsoft is planning to release the Coco Framework to Open Source in early 2018. Along with their open approach to Blockchain, Coco will be compatible with any Blockchain ledger protocol, and will be able to operate in the cloud as well as on-premises."
Check white paper
--> https://buildazure.com/2017/11/22/introducing-microsoft-coco-framework-for-blockchain/
\section{Corda}
Check introductory + technical white papers
\section{Comparison}
"Comparison of Ethereum,
Hyperledger Fabric and
Corda" -> Frankfurt school article
