\chapter{Blockchain and its applicability to the industry}
\label{chap:blockchain-applicability}

Here, we talk about x, y, z.

\section{Similar existing applications}

\section{Advantages of Blockchain Integration}
Introductory text explaining that in general it is very advantageous.

The most general advantages are:

\begin{itemize}
\item Less error prone to manual data entries, especially when combined with IoT and other automated processes.
\item Less governance costs for exchanging info and etc, allowing for higher efficiency and faster times at processing the information (enhancing cost effectiveness)
 \item Enhancing security of transactions
\item Other identified benefits of Digital Supply Chain (DSC) include reduced
product or service costs, creating competitive
advantage and barriers to competition, reduced supply
chain lead times and increased flexibility in supply
chain design. %[21].
\item Reducing internal management costs, increasing efficiency and sustaining
competitiveness.
\end{itemize}

[CITE DSC ARTICLE HERE?]

There are, however, a few more practical descriptions of ways in which a blockchain would act to improve the flow of a supply chain.

\subsection{Ledger and Information Storage}
Describe in which particular way a Ledger would help, citing sources and particular use cases, if possible.
      
\subsection{Smart Contracts}
Describe in which particular way Smart Contracts would help, citing sources and particular use cases, if possible. 
        
\subsection{Transactions}
Describe in which particular way a Ledger would help, citing sources and particular use cases, if possible.

\section{Weaknesses and Challenges of Blockchain Application}
->Check image from the other article
->Other article talking about the throughput and latency trade-off.
\subsection{Scalability Concerns}
- Blockchain might get too big
\subsection{Lack of Interoperability Standards}

\subsection{Maintenance Costs}
- Electricity, etc
        
\subsection{Information Inaccuracy}        
- Isolated nodes and forks might cause inaccuracy. Might be related to scalability, in some way.

\section{Integration Models}
CHECK https://modum.io/system/

\paragraph{Point-to-point} EDI B2B - "All
integration has to be design between all companies and
the number of processes integrated into the system."
        
\paragraph{One-to-many entities} Hub B2B - "A single company can establish business process
connections with intermediates."
\paragraph{Many-to-many entities} Cloud B2B - "From an academic perspective, many-to-many integration models like private cloud (ERP/Hub companies), public cloud (ERP/SME) and public cloud (Intermediate/Blockchain) are the most cost-effective integration models."
