\chapter{Problem Statement}
\label{chap:supply-chain-problems}
\minitoc \mtcskip \noindent 

This chapter focuses on explaining the objectives of this thesis, by defining the statements that are being defended, as well as the approach that will be taken to determine whether these statements are valid or not.

After having previously mentioned some background information about Blockchain technology and frameworks, as well as about supply chain management and supply chain issues, it is now time to focus on what these issues mean. Therefore, a possible way to overcome these issues through the means of Blockchain technology shall be formulated and tested.

\section{Objectives}

\subsection{Main Points of Focus}
\label{sec:points-of-focus}
In SCM, a product's life cycle can be roughly divided into the many phases the product goes through, down from the raw materials up until the finished product ends in the hands of a consumer. Starting in the raw materials, these undergo iterations of processing and shipment, traveling from one place to another, while being transformed in successively more refined products \todo{fcorreia: da forma como está escrito dás a entender que é obrigatório serem transformados. na frase que vêm a seguir tentas clarificar isso, mas pode ser confuso se os leitores tiverem percebido o contrário nesta frase} and changing owners. This holds true for any product in any kind of industry, and even the simplest of products which might not require any processing (for instance, fresh produce), have to be shipped from their place of origin to the place where they will be sold.



\textbf{The improvement of the management of this life cycle is the main objectives of this thesis. This improvement, however, has many points of focus. Some were already briefly introduced in sections \ref{supply_chains} and \ref{supply_chain_challenges}, from which we can extract the following points as the most important.}

\todo{fcorreia: Concordância entre plural e singular ("is" vs "objectives")}

% Assumptions? Some statements about supply chain efficiency;
\begin{itemize}
% Speed of delivery
\item \textbf{Speed of delivery}
The effects of the evolution of SCM throughout the last century are visible to everyone. Products are bought and shipped from one side of the globe to the other in a matter of weeks or sometimes even days. Whether this is fast enough or not is a question that can not be entirely answered in one collective voice. 

One thing is certain: the world around us moves quickly, and in the freneticism and frenzy of our lives, sometimes weeks or days aren't enough. \todo{fcorreia: afirmações absolutas são quase sempre contra-argumentáveis...  :-)} \textbf{The faster the products arrive to their customer, the faster the customer can satisfy their needs.} \todo{concordancia pural singular: "customer" vs "their"} This holds true not only for the final customer of a product, but also for any enterprise that provides products and services to other enterprises, be it in the role of supplier, manufacturers, distributors or retailers. \todo{fcorreia: não será melhor chamar-lhe antes "buyer" em vez de "customer", acho que dá menos a entender que te possas estar a referir ao cliente final}

\item \textbf{Synchronization}
%Synchronization - specify why it is important
Many times, the data from a company is synchronized with its own servers and software, in protocols and data formats that can only be understood by that specific piece of software. If many companies share this same software, then they can easily integrate the information between themselves.

The real problem occurs when the companies have no common ground and the data is not transmittable in an automatic way, leading to a lot of unnecessary manual work to export the data from one system and import it into another. Though there may be many causes for this, the logic assumption would be that this problem may be originated mainly the following:
\begin{itemize}
\item \textbf{Lack of development of data integration standards in the supply chain industry.}
\item \textbf{Lack of a common technology to store all data, from where each company could have their own software extract the information from.}
\end{itemize}

\item \textbf{Tracking}
%Tracking - specify why it is important
During a product's lifetime, a lot of alterations occur, and sometimes, the records about the origins of the products are lost, falsified, or flat out not registered. This leads to unreliability in the goods the consumers use everyday, and sometimes even to safety hazards. Often, the products are not what they were originally meant to be, or do not comply with quality standards.

For this reason, it is of the utmost importance that the products are tracked since their origin, right up until the delivery to the final customer, as well as the conditions they are shipped in and the transformations they suffer.

\item \textbf{Security}
%Security - specify why it is important
This point is one of the most important to deal with, as security is comprised of many aspects, such as: who to authorize to access the information and how to restrict this, what authentication methods should be used, how to accurately detect and prevent fraud, etc. 

Information in a supply chain is highly sensitive and not only should the people who access it be controlled, but also the people who generate it. On one hand, most enterprises (or groups of enterprises) compete amongst themselves to make the most sales, the most deliveries and have the fastest product cycles. \textbf{All the information that is generated in the process might be too sensitive to share, in order to keep the edge on the competition}.
On the other hand, \textbf{the information that is generated and inserted into any system should also be controlled and verified, in order to prevent both human error and fraud attempts}.

On the other hand
\end{itemize}

\subsection{Possible Solutions}
% Mention a possible solution that might or not be better
While these previous points of focus are not problems themselves, their improvement will greatly benefit any industry as well as the consumers of these industries. As such, the actual problem here can be narrowed down to \textbf{finding a way to satisfy these needs for improvement through technological means.}

Some of the most common and traditional solutions include distributed databases, a commonly debated paradigm. Recently, cloud-based solutions for integrating supply chain software, as well as enterprise planning software have been taking the lead. While these might satisfy the need to store the data in a way that can be easily retrieved, they are sometimes costly and have a rather narrow scope of integration. Distributed databases are not very scalable if we take think about maintaining the data of hundreds of companies. The same can be said of cloud-based solutions. Scalability is not the only concern, security is as well. These technologies, however, are already being used, and it is time to analyze if there is a \textbf {good alternative}.%BACK THIS UP WITH REFERENCES

So, is there any other tool or technology that can be applied to SCM, in order to satisfy the need for improvement, one that is scalable, as well as secure?
In many ways, Blockchain is similar to a distributed database, and it can even be integrated with the cloud for a mixed solution (the best of both worlds?), so there is a need to investigate if it might or might not be a fit solution for this optimization problem.

\subsection{Thesis Statement}
\label{subsec:thesis-statement}
The main objective has already been defined: to improve the security traits, tracking of goods and processes, information synchronization, and possibly speed of delivery of the supply chain, along with other minor attributes. A seemingly good alternative that stands out is Blockchain. What remains to be answered, though, is if these attributes are really the right requirements to focus on, and if Blockchain can really fill them, as a distributed architecture.

% MAIN THESIS we are defending defined here
%TODO: SHOULD IT BE IN QUESTION FORM, OR AFFIRMATION?
Therefore, the main statement that this thesis defends is: 

\par \textbf{\textit{"Is Blockchain a good architectural design for the Supply Chain Management domain?"}}

% THESIS branches: all the possibilities that might happen
This statement may be based on many assumptions, which gives rise to some more questions. For instance, we are assuming that the points of focus from section \ref{sec:points-of-focus} are really the most important ones, given the background information that was collected.

Thus, the questions that need to be answered first, in order to reach a conclusion towards the main thesis statement are the following:
\begin{enumerate}
\item \textbf{What supply chain issues and requirements do the experts really find the most important?}
\item \textbf{What is the Blockchain tool or framework most adequate to the development of an architecture that can support these requirements?}
\item \textbf{Is it possible to build a feasible architectural design, by using such a tool implement all these requirements?}
\end{enumerate}

These questions are sequential, meaning that, in order to answer one of them, we have to answer the previous question. Only in the end can we reach a definitive conclusion, though the sub-conclusions are also interesting to analyze and a contribute themselves to this area.

\section{Approach}
% What if no possibility works or we can't ascertain the main possibility? Check other ones!

% Construct the story of how the thesis came along! IMPORTANT (switch order?)
%TODO: ANSWER THESE LAST 2 POINTS

% To test the thesis, we will divide the work in 2 parts: survey and prototype;
To answer these questions from section \ref{subsec:thesis-statement}, the work of this dissertation was divided into two main parts, each of them comprising a chapter:
\begin{enumerate}
\item \textbf{Survey Research - Supply Chain Issues Validation and Requirements Elicitation}
\item \textbf{Software Engineering - Architectural Design and Implementation of a Prototype}
\end{enumerate}

% Each one focuses on supporting a specific part of the thesis statement;
Each of these focuses on reaching a conclusion towards the answers that underlie the thesis statement.

\subsection{Survey Research - Supply Chain Issues Validation And Requirements Elicitation}
\label{sec:survey-approach}
% The survey will serve to support "..." and take conclusions about whether "..."
The first question to answer in order to reach any conclusion is \textbf{\textit{"What supply chain issues and requirements do the experts really find the most important?"}}. As already mentioned, the other questions depend on the answers that we reach for this question.

%TODO: should the verbs be in the past, present or future here?
% What did you choose to do?
The proposed way that was chosen to get an answer was an online \textbf{survey}. The survey serves the following purposes:
\begin{itemize}
\item Collecting quantitative data on the relevance of the issues that supply chain management suffers from as well. 
\item Collecting quantitative and qualitative data on which are the major points of improvement and compare their relative importance.
\item Collecting quantitative and qualitative data on which issues and improvement points the experts think Blockchain can help the most with, and which are already taken care of by other solutions.
\item Correlate some of the data collected in the previous point and reach some extra conclusions that might help decide on the validity of the results.
\end{itemize}

% Why did you choose it?
It was designed to be answered by people with experience in the field of Supply Chain, with knowledge about Blockchain being optional but appreciated. These are the opinions that have the most importance on this field, and these are also the people that interact with the systems in question and can more accurately pinpoint the points of failure and improvement.

The survey was distributed over the internet, through relevant media and social forums, as well as through direct contact with professionals from the area. It was shared on some telegram channels of projects that apply Blockchain to the supply chain (most of which mentioned in the state of the art), on Reddit, through their supply chain and logistics forums, as well as on supply chain focused forum websites. It was also distributed to professionals through messages on LinkedIn (with a focus on managers), personally and through email.

In conclusion, the goal of the survey is to validate some assumptions and direct the dissertation towards the most important of the supply chain management problems.

\subsection{Software Engineering - Architectural Design and Implementation of a Prototype}
% The prototype will serve to support "...", along with the requirements that were written based on the background research and literature review; (do i have to rewrite part of the requirements?) 

%TODO: should the verbs be in the past, present or future here?
Having answered the question about which are the most important aspects of supply chain to focus on improving, this section is focused on applying this knowledge to answer the other two final questions: \textbf{\textit{"What is the Blockchain tool or framework most adequate to the development of an architecture that can support these requirements?"}} and 
\textbf{\textit{"Is it possible to build a feasible architectural design, by using such a tool implement all these requirements?"}}

The state of the art already provided some information towards the answer to the first of these questions, through the comparison of frameworks. Therefore, and taking the results of the survey into account, a brief analysis is undertaken to make a decision.

Finally, and to answer the final question about the possibility and feasibility of building a blockchain-based architectural design for supply chain management, a software engineering approach is undertaken, using the chosen platform. 

%TODO: justify the choice of platform by the ease of use as well?

This approach is divided into the following phases:
\begin{enumerate}
\item \textbf{Requirement Elicitation and validation} - through the literature review research and survey results 
\item \textbf{Design} - using the requirements, building a model that can implement these
\item \textbf{Implementation} - program the system according to the design, as close as possible without alterations
\item \textbf{Validation} - check if the built system satisfies the initial requirements fully, and if otherwise, explaining why not
\end{enumerate}

After this approach is finished, the results are analyzed qualitatively, as to which use cases are implementable and usable or not and as to what were the limitations found because of the various decisions taken. Taking the various points of this analysis into consideration will allow for some conclusions to be taken in reference to the remaining question.
% It will be conducted in the following way: 1. Requirements 2. Design 3. Implementation 4. Testing 5. Evolution

%It follows a software engineering development agile pattern with phases 1 through 4 being iterated through;

% Mention that survey didnt or possibly wouldnt come along soon enough to support a change in ALL the requirements, but some

\subsection{Conclusions}

After having answered all of the three questions that underlie the thesis statement, it is possible to give an answer, though future work may eventually bring different answers, since Blockchain is a technology which is seeing great and fast developments.

% Comments to pay attention to!

%\todo{fcorreia: the technologies/techniques/approaches that make a blockchain are not new, I think you could even call them "traditional". They become more interesting when put together though.}

%\todo{fcorreia: the last sentence of the above paragraph seems like a bit of a stretch. I think we can imagine alternative ways to do all of this without a blockchain. I don't think we want to compare blockchains with existing technologies, we want to see if blockchains *are* a good choice to implement supply chains management software that fits well with today's requirements (even if there may be other ways of achieving the same -- i.e., without a blockchain). WDYT?}