
\section{Conclusions}

\subsection{Survey Conclusions}
%Conclude that the prototype must focus on: security and traceability, as these are the items that the respondent's focused the most on; though these 2 are the focus, features such as X, Y, Z must not be forgotten, since they ranked high on both information system features and blockchain applicability to the SC; A good blockchain design for the SC should not only feature NEW use cases that the blockchain brings to SC, like financial transactions, but also feature improved features from the already existing systems.

Having analyzed all the groups of questions from the survey, it should now be possible to have an answer for the first question of the thesis sub-statements, presented in the problem statement: \textit{"What supply chain issues, improvements and requirements do the experts really find the most important?"}.

Most of the conclusions for the survey were summarized in the analysis of question group 4. These conclusions included the most important issues of the supply chain, points of improvement, blockchain features and information system functionalities important to the design.


\par \textbf{Issues} - These include \textbf{inventory management}, \textbf{quality assurance}, \textbf{} and \textbf{lack of accurate and timely data}. This last item was confirmed by the respondents to have a correlation to the lack of good integration and synchronization tools and to be one of the possible causes for the difficulties in planning management and product cycle delays.

\par \textbf{Point of improvement} - These include \textbf{traceability}, \textbf{supply control}, \textbf{fraud detection} and \textbf{synchronization}. These items reflect themselves on the feature requirements that were elicited. The results can therefore be crossed with the points of improvement to make more refined logical groups of requirements:

\par \textbf{Important Features} - The most important features, gathered from a junction of information system features and blockchain features, are summarized in Table \ref{table:elicited-requirements-survey}.

%%% TABLE START %%%%%%%%%%%
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    \textbf{Area}                                                                                              & \textbf{Requirements}                                                                                                              \\ \hline
    \multirow{3}{*}{Security}                                                                                  & Security according to the latest requirements                                                                                      \\ \cline{2-2} 
                                                                                                               & Controlled access for the users                                                                                                    \\ \cline{2-2} 
                                                                                                               & Secure data storage                                                                                                                \\ \hline
    \multirow{4}{*}{Traceability}                                                                              & Regulatory auditing                                                                                                                \\ \cline{2-2} 
                                                                                                               & Fraud detection                                                                                                                    \\ \cline{2-2} 
                                                                                                               & Asset management                                                                                                                   \\ \cline{2-2} 
                                                                                                               & Real-time tracking information                                                                                                     \\ \hline
    \multirow{3}{*}{Synchronization}                                                                           & Interoperability between systems                                                                                                   \\ \cline{2-2} 
                                                                                                               & Development of industry standards                                                                                                  \\ \cline{2-2} 
                                                                                                               & \begin{tabular}[c]{@{}l@{}}Real-time sharing of information with partners, leading to \\ better working relationships\end{tabular} \\ \hline
    \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Transaction \\ Enforcement and\\ Financial domain\end{tabular}} & Financial transactions                                                                                                             \\ \cline{2-2} 
                                                                                                               & Enforceable contracts (smart contract functionality)                                                                               \\ \hline
    \end{tabular}
    \caption{Elicited requirements grouped by improvement area of focus.}
    \label{table:elicited-requirements-survey}
    \end{table}
%%% TABLE END %%%%%%%%%%%%%%%

These are important contributions from the experts of the area, though with a bigger sample, the answers would have been more representative. The next chapter will focus on these requirements as the major points of focus for the design.


%subsection: relate to what the already existing projects do
\subsection{Comparison to the state-of-the-art projects}
Most of the projects analyzed in the state-of-the-art, thought they use a multitude of different frameworks and custom networks, also do not focus on satisfying all of the requirements, but mostly a subset of them. Most of the projects specialize only in 1 problem area, like traceability, instead of going for an all-rounded concept.

\par \textbf{CargoX} This project focuses somewhat on Secure Data Storage, Enforceable Contracts and Security, even though in a limited way, since the data stored is not for any asset or document, but specifically for bill of lading documents. Additionally, it lacks a lot in the traceability items.

\par \textbf{Eximchain} It attempts to tackle all of the areas: Traceability, Security, Synchronization, Contracts and Finance. Though it promises a lot in its presentations, the actual whitepaper and technical documents focus mostly on the financial and contractual aspects and do not explain how the other aspects will be achieved in detail. The product looks promising for this area, by focusing all the requirements in a way that is claimed to be efficient, with custom networks and consensus algorithms and protocols. However, and very importantly, Eximchain's product has not yet been proven to work. The project has 3 proof-of-concepts planned in their roadmap, each focusing on separate areas, but none has been presented yet.

\par \textbf{OriginTrail} This project boasts of its strong traceability capabilities, mainly for asset management, auditing and fraud detection. It is a specific project, but it does not fit all of the requirements above,  as it misses the financial transactions and some security aspects, such as access control. Again, as is the case with Eximchain, the project seems promising, but is yet to prove most of its functionalities, having released proof-of-concepts mostly for the traceability requirements. This seems to be a common element to most of these projects, in that they look promising but take a long time to prove that they can deliver their promises.

\par \textbf{Ambrosus} Focuses a lot on auditing, fraud detection, quality control and traceability in general, so it fills all the traceability requirements. Even though these features are a must, and seemingly the most important, most of the other requirements are not met, especially the financial transactions, asset management and part of the security requirements.

In summary, the existing projects are either very specialized and do not meet all the requirements, or they are very broad in the requirements, but in early stages of development, without proving that they can do what they promise.