
%subsection: relate to what the already existing projects do
\section{Comparison to the state-of-the-art projects}
Most of the projects analyzed in the state-of-the-art, thought they use a multitude of different frameworks and custom networks, also do not focus on satisfying all of the requirements, but mostly a subset of them. Most of the projects specialize only in 1 problem area, like traceability, instead of going for an all-rounded concept.

\par \textbf{CargoX} This project focuses somewhat on Secure Data Storage, Enforceable Contracts and Security, even though in a limited way, since the data stored is not for any asset or document, but specifically for bill of lading documents. Additionally, it lacks a lot in the traceability items.

\par \textbf{Eximchain} It attempts to tackle all of the areas: Traceability, Security, Synchronization, Contracts and Finance. Though it promises a lot in its presentations, the actual whitepaper and technical documents focus mostly on the financial and contractual aspects and do not explain how the other aspects will be achieved in detail. The product looks promising for this area, by focusing all the requirements in a way that is claimed to be efficient, with custom networks and consensus algorithms and protocols. However, and very importantly, Eximchain's product has not yet been proven to work. The project has 3 proof of concepts planned in their roadmap, each focusing on separate areas, but none has been presented yet.

\par \textbf{OriginTrail} This project boasts of its strong traceability capabilities, mainly for asset management, auditing and fraud detection. It is a specific project, but it does not fit all of the requirements above,  as it misses the financial transactions and some security aspects, such as access control. Again, as is the case with Eximchain, the project seems promising, but is yet to prove most of its functionalities, having released proof of concepts mostly for the traceability requirements. This seems to be a common element to most of these projects, in that they look promising but take a long time to prove that they can deliver their promises.

\par \textbf{Ambrosus} Focuses a lot on auditing, fraud detection, quality control and traceability in general, so it fills all the traceability requirements. Even though these features are a must, and seemingly the most important, most of the other requirements are not met, especially the financial transactions, asset management and part of the security requirements.

In summary, the existing projects are either very specialized and do not meet all the requirements, or they are very broad in the requirements, but in early stages of development, without proving that they can do what they promise.